A generalized definition of multidimensional item response theory parameters

### 2024-09-06 output/Main_text.Rmd
Reverts rendering Figure 1 from SVG to PNG

library(here)
library(knitr)
library(patchwork)
library(ggplot2)
library(rstudioapi)
library(rsvg)    # Used by {knitr} and {ggplot2} to render the figure to SVG;
library(svglite) #   added to prevent {renv} from reporting inconsistent state.

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  cache    = FALSE,
  dev      = "svg"
)

>>>>

library(here)
library(knitr)
library(patchwork)
library(ggplot2)
library(rstudioapi)
library(svglite) # Used by {knitr} and {ggplot2} to render the figure to SVG;
                 #   added to prevent {renv} from reporting inconsistent state.

@@

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      = 1200L,
  dev.args = list(type = "cairo-png")
)
